\documentclass[a4paper,12pt]{book}
%\linespread{2.}
\usepackage{latexsym}
\usepackage{amssymb}
\usepackage{amsmath}
%\usepackage [latin1]{inputenc}
\usepackage{verbatim}
\usepackage{array}
\usepackage{color}
\pagestyle{plain}
\usepackage{graphicx}

\begin{document}
\section*{R. A. Broglia, Publications 2016--2017}
\begin{itemize}
\item Heike I. R\"osner, Martina Caldarini, Andreas Prestel, Maria A. Vanoni, Ricardo A. Broglia, Alessandro Aliverti, Guido Tiana, and Birthe B. Kragelund \textit{Cold Denaturation of the HIV‐1 Protease Monomer}, Biochemistry \textbf{56} (2017) 1029
\item Ricardo A. Broglia \textit{Nuclear Structure then and now: 40 years of the 1975 Nobel
Prize in Physics}, Ann. Phys. \textbf{528} (2016) 444
\item F. Barranco, G. Potel,  R. A. Broglia,  and E. Vigezzi  \textit{Structure and Reactions of
$^{11}$Be:
Many--Body Basis for Single--Neutron Halo}, Phys. Rev. Lett.\textbf{119} (2017) 082501
\item P.F. Bortignon and R.A. Broglia \textit{Elastic response of the atomic nucleus in gauge
space: Giant Pairing Vibrations}, Eur. Phys. J. A\textbf{52} (2016) 280
\item P.F. Bortignon and R.A. Broglia \textit{Challenges in the description of the atomic nucleus: Unification
and interdisciplinarity}, Eur. Phys. J. A \textbf{52} (2016) 64
\item A. Idini, G. Potel, F. Barranco, E. Vigezzi, and R. A. Broglia \textit{Dual Origin of Pairing in Nuclei}, Physics of Atomic Nuclei \textbf{79} (2016) 807
\item R A Broglia, P F Bortignon, F Barranco, E Vigezzi, A Idini and
G Potel \textit{Unified description of structure and
reactions: implementing the nuclear field
theory program}, Phys. Scr. \textbf{91} (2016) 063012
\item G. Potel, A. Idini,  F. Barranco, E. Vigezzi, and R. A. Broglia \textit{From bare to renormalized order parameter in gauge space: Structure and reactions}, Phys. Rev. C \textbf{96} (2017) 034606
\end{itemize}
\end{document}













